---
title: "Genetic associations of protein-coding variants in human disease"
author: "Christopher Foley and Benjamin Sun"
date: "`r Sys.Date()`"
output:
  pdf_document: default
  html_document: null
  toc: yes
  toc_depth: 2
vignette: |
  %\VignetteIndexEntry{mrclust} 
  %\VignetteEngine{knitr::rmarkdown} 
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.width = 5, 
  fig.height = 4
)
```

```{r setup}
library(AllelicHeterogenitySimulator)
```


# Introduction


The vignette provides code and some


# Installation


```{r, echo=F}
options(warn = -1)
```

```{r, eval=F}
install.packages("devtools", repos='http://cran.us.r-project.org')
library(devtools)
install_github("cnfoley/Sun-et-al-2021-protein-coding-variants-in-human-disease", build_vignettes = FALSE)
install_github("cnfoley/mrclust", build_vignettes = TRUE)
library(AllelicHeterogenitySimulator)
browseVignettes("AllelicHeterogenitySimulator")

```

# Reproducing the allelic heterogeneity simulator 

...

## Replicating Figure 1d 

Here we replicate the results from...We begin by
loading the package and the SBP/CAD summary data. These data are avaiable with
the package and can be found by typing

```{r}
library(AllelicHeterogenitySimulator)
betas <- AllelicHeterogenitySimulator::betas
head(betas)
```

In the... (UKB) and (FG). A description of these data is found by
typing:

```{r}
?AllelicHeterogenitySimulator::betas
```

The function "allelic_het_simulator" (minimally) requires the following summary data
information: 

## Running the simulator 


To run ...      

```{r}
############################
########### SBP-CAD analysis
############################

results = allelic_het_simulator(betas = betas, n_simulated_datasets = 2);

```
